---
title: "What did HOP Airdrop Claimers do after?"
author: "Charliemarketplace"
date: "`r Sys.Date()`"
output:
  html_document:
    css: "styles.css"
    includes:
      in_header: header.html
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

FlipsideCrypto's Research is open source. Check out all the code for this report [here](https://github.com/FlipsideCrypto/hopdrop) on github.

# Intro

This is an example analysis to identify how addresses that (1) claimed HOP tokens 
used their HOP, including:

General Airdrop Actions: 

- Retained their claim
- Transfer their claim
- Sell their claim on a DEX
- Buy more HOP on a DEX
- Deposit their claim into DEX Liquidity Pool(s)

Airdrop specific Actions:
- Earn more HOP via Hop cross-chain LP

# Airdrop Recipients

```{r, warning = FALSE, message = FALSE}
library(shroomDK)
library(reactable)
library(ggplot2)
library(plotly)
library(lubridate)
library(dplyr)

hop_claimers_query <- {
  "
  with airdrops AS (
 -- HOP Claim
 SELECT LOWER('0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc') as CONTRACT_ADDRESS, 'TOKENSYMBOL' as SYMBOL, LOWER('0x76122903') as ORIGIN_FUNCTION_SIGNATURE FROM DUAL
),

airdrop_claimants AS (
SELECT TX_HASH, CONTRACT_ADDRESS, FROM_ADDRESS, TO_ADDRESS, SYMBOL, ORIGIN_FUNCTION_SIGNATURE, AMOUNT, AMOUNT_USD
  FROM ethereum.core.ez_token_transfers
WHERE CONTRACT_ADDRESS IN (SELECT CONTRACT_ADDRESS FROM airdrops) AND 
ORIGIN_FUNCTION_SIGNATURE IN (SELECT ORIGIN_FUNCTION_SIGNATURE FROM airdrops) AND 
BLOCK_NUMBER <= 16400000
)

SELECT TO_ADDRESS as user_address, contract_address as token_contract, symbol as token_symbol, 
COUNT(*) as n_airdrops_claimed, SUM(AMOUNT) as claimed_token_volume, SUM(AMOUNT_USD) as claimed_usd_volume 
FROM airdrop_claimants
GROUP BY user_address, token_contract, token_symbol
  "
}

hop_claimers <- auto_paginate_query(hop_claimers_query, api_key = readLines("api_key.txt"))

```

Looking at all HOP claimers on or before block 16400000 (Jan 13 2023) for reproducibility 
of analysis there are `r length(unique(hop_claimers$USER_ADDRESS))` unique addresses that claimed HOP 
with a median claim amount of `r median(hop_claimers$CLAIMED_TOKEN_VOLUME)` and an average of 
`r mean(hop_claimers$CLAIMED_TOKEN_VOLUME)`.

```{r, warning = FALSE, message = FALSE}
plot_ly(data = hop_claimers, x = ~CLAIMED_TOKEN_VOLUME, type = 'histogram') %>% 
  layout(
    title = list(text = "The typical airdrop was ~1200 HOP", y = 0.95), 
      xaxis = list(title = "# Tokens Claimed", range = c(0,50000)),
         yaxis = list(title = "# of Claimants in Range", range = c(0, 10000)))

```

## General Churn 

Getting claimer balances as of BLOCK_NUMBER = 16400000 to identify how quickly balances of recipients fell to < 1 (i.e., 0 or dust), focusing specifically on those that claimed >= 1 HOP (ignoring those that claimed dust amounts).

```{r, warning = FALSE, message = FALSE}

bal_query <- {
  "
 with airdrops AS (
 -- HOP Claim
 SELECT LOWER('0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc') as CONTRACT_ADDRESS, 'TOKENSYMBOL' as SYMBOL, LOWER('0x76122903') as ORIGIN_FUNCTION_SIGNATURE FROM DUAL
),

airdrop_claimants AS (
SELECT TX_HASH, CONTRACT_ADDRESS, FROM_ADDRESS, TO_ADDRESS, SYMBOL, ORIGIN_FUNCTION_SIGNATURE, AMOUNT, AMOUNT_USD
  FROM ethereum.core.ez_token_transfers
WHERE CONTRACT_ADDRESS IN (SELECT CONTRACT_ADDRESS FROM airdrops) AND 
ORIGIN_FUNCTION_SIGNATURE IN (SELECT ORIGIN_FUNCTION_SIGNATURE FROM airdrops) AND 
BLOCK_NUMBER <= 16400000
),

claimant_details AS (SELECT TO_ADDRESS as user_address, contract_address as token_contract, symbol as token_symbol, 
COUNT(*) as n_airdrops_claimed, SUM(AMOUNT) as claimed_token_volume, SUM(AMOUNT_USD) as claimed_usd_volume 
FROM airdrop_claimants
GROUP BY user_address, token_contract, token_symbol),

typical_users AS (
SELECT * FROM claimant_details WHERE 
claimed_token_volume >= 1
),

--user_address | token_contract | token_symbol | tw_token_balance
block_tracked AS (
    SELECT USER_ADDRESS as address,
           CONTRACT_ADDRESS as token_address,
           symbol as token_symbol,
           BLOCK_NUMBER as block,
	       BLOCK_TIMESTAMP,
           PREV_BAL as old_value,
           CURRENT_BAL as new_value
    FROM ETHEREUM.CORE.EZ_BALANCE_DELTAS
    WHERE BLOCK_NUMBER <= 16400000
    AND token_address = LOWER('0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc') 
    AND USER_ADDRESS IN (SELECT user_address FROM typical_users)
  ),
  
-- group by holder-token
-- order by block desc
-- pick most recent block
-- get holders w/ address type label in case it is a contract
token_holder AS (
SELECT *, ROW_NUMBER() over (partition by address, token_address, token_symbol order by block DESC) as rownum
FROM block_tracked
)
  
SELECT  address as user_address, token_address as token_contract, token_symbol, new_value as token_balance,
  block as last_balance_change_block, block_timestamp as last_balance_change_date
FROM token_holder
    WHERE rownum = 1
    
"
}

claimer_balance <- auto_paginate_query(query = bal_query, api_key = readLines('api_key.txt'))

```

```{r, warning = FALSE, message = FALSE}

hop_balance_0 <- claimer_balance %>% 
  filter(TOKEN_BALANCE < 1) %>% 
  mutate(churn_date = ymd(as.Date(LAST_BALANCE_CHANGE_DATE))) %>% 
  group_by(churn_date) %>% 
  summarise(num_churners = n())

ymonth <- function(date){
  y = year(date)
  m = month(date)

  if(nchar(m) == 1){
    m <- paste0("0",m)
  }
  
  return(paste0(y,"-",m))
}

hop_balance_0$churn_month <- sapply(hop_balance_0$churn_date, ymonth)

hop_month_churn <- hop_balance_0 %>% group_by(churn_month) %>% 
  summarise(total = sum(num_churners))

```

Among the `r round(100 * sum(claimer_balance$TOKEN_BALANCE < 1)/nrow(claimer_balance), 2)`% of claimants (who claimed at least 1 HOP) who no longer hold their HOP (hold < 1 HOP as of the timestamp), `r hop_month_churn$total[hop_month_churn$churn_month == '2022-06']` moved/sold/deposited in June 2022.

```{r, warning = FALSE, message = FALSE}
plot_ly(data = hop_month_churn,
        x = ~total, 
        y = ~churn_month, 
        type = 'bar') %>% 
  layout(
    title = list(text = "Of the 62% that dumped, most did so immediately.",
                 y = 0.95),
    xaxis = list(title = "# Claimants Cashing Out"),
    yaxis = list(title = "Year-Month")
  )

```

## Accumulatooooors

```{r, warning = FALSE, message = FALSE}
hop_merge <- merge(claimer_balance[, c("USER_ADDRESS","TOKEN_BALANCE")], 
                     hop_claimers[, c("USER_ADDRESS", "CLAIMED_TOKEN_VOLUME")],
                   by = "USER_ADDRESS", all.x = TRUE)

```

`r round(100*ecdf(hop_merge$CLAIMED_TOKEN_VOLUME)(5000), 2)`% of claimers, claimed 5,000
or less HOP. Focusing on this group:

```{r, warning = FALSE, message = FALSE}

plot_ly(alpha = 0.45,
        data = hop_merge %>% filter(CLAIMED_TOKEN_VOLUME <= 5000),
        x = ~(TOKEN_BALANCE - CLAIMED_TOKEN_VOLUME),
        nbinsx = 50000,
        name = "",
        type = "histogram"
)  %>%
  layout(
    barmode = "overlay",
    title = list(text = "Change in HOP Balance among Typical Claimers (<= 5K claimed)", y = 0.975),
    xaxis = list(title = "HOP Accumulated (Current - Claimed)", range = c(-5000, 5000)),
    yaxis = list(title = "# Claimers", range = c(0, 800))
  )

```

- `r sum(hop_merge$TOKEN_BALANCE > hop_merge$CLAIMED_TOKEN_VOLUME)` of the typical claimers (<= 5k HOP claimed)
(`r round(100*sum(hop_merge$TOKEN_BALANCE > hop_merge$CLAIMED_TOKEN_VOLUME)/nrow(hop_merge), 2)`%) currently 
have **more** HOP than they claimed; 

- `r sum(hop_merge$TOKEN_BALANCE == hop_merge$CLAIMED_TOKEN_VOLUME)` of the typical claimer (<= 5k HOP claimed)
(`r round(100*sum(hop_merge$TOKEN_BALANCE == hop_merge$CLAIMED_TOKEN_VOLUME)/nrow(hop_merge), 2)`%) have the *exact* same amount as they claimed.

# Actions after Claim 

Breaking down how recipients did:

- Retained their claim
- Transfer their claim
- Sell their claim on a DEX
- Buy more HOP on a DEX
- Deposit their claim into DEX Liquidity Pool(s)

```{r, warning = FALSE, message = FALSE}

# identify the liquidity pools 
hop_pools_query <- {
  "
-- HOP liquidity pools 
SELECT POOL_ADDRESS, POOL_NAME, PLATFORM, TOKEN0, TOKEN0_SYMBOL, TOKEN1, TOKEN1_SYMBOL FROM 
ethereum.core.dim_dex_liquidity_pools WHERE
TOKEN0 = '0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc' OR TOKEN1 = '0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc'
  "
} 

hop_lps <- auto_paginate_query(hop_pools_query, api_key = readLines("api_key.txt"))

# superset of lp deposits, lp withdrawals, trades, simple_transfers
hop_transfers_query <- {
  "
  -- Airdrop claimants
   with airdrops AS (
 -- HOP Claim
 SELECT LOWER('0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc') as CONTRACT_ADDRESS, 'TOKENSYMBOL' as SYMBOL, LOWER('0x76122903') as ORIGIN_FUNCTION_SIGNATURE FROM DUAL
),

airdrop_claimants AS (
SELECT TX_HASH, CONTRACT_ADDRESS, FROM_ADDRESS, TO_ADDRESS, SYMBOL, ORIGIN_FUNCTION_SIGNATURE, AMOUNT, AMOUNT_USD
  FROM ethereum.core.ez_token_transfers
WHERE CONTRACT_ADDRESS IN (SELECT CONTRACT_ADDRESS FROM airdrops) AND 
ORIGIN_FUNCTION_SIGNATURE IN (SELECT ORIGIN_FUNCTION_SIGNATURE FROM airdrops) AND 
BLOCK_NUMBER <= 16400000
), 

claimants AS (
SELECT TO_ADDRESS as user_address, contract_address as token_contract, symbol as token_symbol, 
SUM(AMOUNT) as claimed_token_volume
FROM airdrop_claimants
GROUP BY user_address, token_contract, token_symbol
),

transfers AS (
SELECT TX_HASH, FROM_ADDRESS, TO_ADDRESS, CONTRACT_ADDRESS, 
AMOUNT
FROM ethereum.core.ez_token_transfers WHERE 
CONTRACT_ADDRESS = '0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc' AND
(FROM_ADDRESS IN (SELECT user_address FROM claimants) OR 
 TO_ADDRESS IN (SELECT user_address FROM claimants)) AND 
BLOCK_NUMBER <= 16400000
     )

SELECT TX_HASH, FROM_ADDRESS, 
  CASE
    WHEN FROM_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('gnosis safe address')) THEN 'gnosis safe'
    WHEN FROM_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('contract address')) THEN 'contract'
    WHEN FROM_ADDRESS IN (SELECT DISTINCT address FROM flipside_prod_db.crosschain.address_labels WHERE label_type = 'cex') THEN 'EOA-cex'
    WHEN FROM_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('active on ethereum last 7')) THEN 'EOA'
    ELSE 'EOA-0tx'
END as FROM_ADDRESS_TYPE,
TO_ADDRESS, 
  CASE
    WHEN TO_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('gnosis safe address')) THEN 'gnosis safe'
    WHEN TO_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('contract address')) THEN 'contract'
    WHEN TO_ADDRESS IN (SELECT DISTINCT address FROM flipside_prod_db.crosschain.address_labels WHERE label_type = 'cex') THEN 'EOA-cex'
    WHEN TO_ADDRESS IN (SELECT DISTINCT address FROM CROSSCHAIN.CORE.ADDRESS_TAGS WHERE BLOCKCHAIN = 'ethereum' AND TAG_NAME IN ('active on ethereum last 7')) THEN 'EOA'
    ELSE 'EOA-0tx'
END as TO_ADDRESS_TYPE,
 CONTRACT_ADDRESS, 
AMOUNT
FROM transfers
  "
}

hop_transfers_by_claimers  <- auto_paginate_query(hop_transfers_query,
                                                  api_key = readLines("api_key.txt"))

# dex trades specifically 
hop_trades_query <- { 
  "
  -- Airdrop claimants
   with airdrops AS (
 -- HOP Claim
 SELECT LOWER('0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc') as CONTRACT_ADDRESS, 'TOKENSYMBOL' as SYMBOL, LOWER('0x76122903') as ORIGIN_FUNCTION_SIGNATURE FROM DUAL
),

airdrop_claimants AS (
SELECT TX_HASH, CONTRACT_ADDRESS, FROM_ADDRESS, TO_ADDRESS, SYMBOL, ORIGIN_FUNCTION_SIGNATURE, AMOUNT, AMOUNT_USD
  FROM ethereum.core.ez_token_transfers
WHERE CONTRACT_ADDRESS IN (SELECT CONTRACT_ADDRESS FROM airdrops) AND 
ORIGIN_FUNCTION_SIGNATURE IN (SELECT ORIGIN_FUNCTION_SIGNATURE FROM airdrops) AND 
BLOCK_NUMBER <= 16400000
), 

claimants AS (
SELECT TO_ADDRESS as user_address, contract_address as token_contract, symbol as token_symbol, 
SUM(AMOUNT) as claimed_token_volume
FROM airdrop_claimants
GROUP BY user_address, token_contract, token_symbol
)

SELECT TX_HASH, ORIGIN_FROM_ADDRESS as user_address, PLATFORM as protocol, TOKEN_IN, SYMBOL_IN, AMOUNT_IN,
TOKEN_OUT, SYMBOL_OUT, AMOUNT_OUT
FROM ETHEREUM.CORE.EZ_DEX_SWAPS
WHERE BLOCK_NUMBER <= 16400000 AND 
user_address IN (SELECT user_address FROM claimants) AND 
(TOKEN_IN = '0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc' OR 
 TOKEN_OUT = '0xc5102fe9359fd9a28f877a67e36b0f050d81a3cc')  
  "
  }

hop_trades_by_claimers <- auto_paginate_query(hop_trades_query,
                                                  api_key = readLines("api_key.txt"))

```

## Note on Balance

A claimant has a *current balance*. Because liquidity pools automatically match buys and sells of tokens, 
it is entirely possible for a claimant to have [claimed] + [bought] - [sold] + [received] - [sent] - [deposit] + [withdrawn] HOP tokens and the sum of these values *not* equal their current balance. 

This is because the difference between the [deposit] and [withdrawn] portions of HOP for a liquidity pool position is sold by 
the pool, not the claimant.

Nonetheless, it is still useful to have all of these values available for each claimant to understand 
what they've done after receiving their airdrop.

## Buys & Sales 

Trades among claimants where they bought/sold HOP.

```{r, warning = FALSE, message = FALSE}
buys <- hop_trades_by_claimers %>% 
  filter(SYMBOL_OUT == "HOP") %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(amount_bought = sum(AMOUNT_OUT))
  
sales <- hop_trades_by_claimers %>% filter(SYMBOL_IN == "HOP") %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(amount_sold = sum(AMOUNT_IN))


```

## Deposit into LPs

Transfers to/from known Liquidity Pools that are *not* swaps.

```{r, warning = FALSE, message = FALSE}
deposits <- hop_transfers_by_claimers %>% filter(
  (TO_ADDRESS %in% hop_lps$POOL_ADDRESS) & !(TX_HASH %in% hop_trades_by_claimers$TX_HASH) 
) %>% 
  mutate(USER_ADDRESS = FROM_ADDRESS) %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(amount_deposited_lp = sum(AMOUNT))

withdraws <- hop_transfers_by_claimers %>% filter(
  (FROM_ADDRESS %in% hop_lps$POOL_ADDRESS) & !(TX_HASH %in% hop_trades_by_claimers$TX_HASH) 
) %>% 
  mutate(USER_ADDRESS = TO_ADDRESS) %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(amount_withdrawn_lp = sum(AMOUNT))

```

## Simple Transfers 

Transfers from a claimant to/from an Externally Owned Account (EOA, i.e., NOT a contract), excluding 
known Central Exchange EOAs and including cold storage accounts that have not initiated their own transactions.

```{r, warning = FALSE, message = FALSE}

simple_out <- hop_transfers_by_claimers %>% 
  filter(FROM_ADDRESS %in% hop_claimers$USER_ADDRESS & 
           TO_ADDRESS_TYPE %in% c('EOA', 'EOA-0tx'))  %>% 
  mutate(USER_ADDRESS = FROM_ADDRESS) %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(simple_amount_out = sum(AMOUNT)) 

simple_in <- hop_transfers_by_claimers %>%
  filter(TO_ADDRESS %in% hop_claimers$USER_ADDRESS & 
           FROM_ADDRESS_TYPE %in% c('EOA', 'EOA-0tx')) %>% 
  mutate(USER_ADDRESS = TO_ADDRESS) %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(simple_amount_in = sum(AMOUNT))

cex_transfers_out <- hop_transfers_by_claimers %>% 
  filter(FROM_ADDRESS %in% hop_claimers$USER_ADDRESS & 
           TO_ADDRESS_TYPE %in% c('EOA-cex'))  %>% 
  mutate(USER_ADDRESS = FROM_ADDRESS) %>% 
  group_by(USER_ADDRESS) %>% 
  summarise(cex_transfer_out = sum(AMOUNT))

```

## Airdrop Actions Table 

Merge everything for users (who claimed at least 1 HOP) into final table, swap NAs w/ 0.

```{r, warning = FALSE, message = FALSE}

tbls = list(
  buys, sales, deposits, withdraws, simple_in, simple_out, cex_transfers_out
)

for(i in tbls){
  hop_merge <- merge(hop_merge, all.x = TRUE, y = i, by = "USER_ADDRESS")
  
}

hop_merge[is.na(hop_merge)] <- 0

reactable(
  hop_merge
)

```

# Claimant Category 

Categorizing claimers based on their post-claim activity; note: for users who might qualify for multiple classes,
they are given the *first* class they qualify for. For example, a Dumpooor Intermediary would only be classified as a Dumpoooor:

- Keepooooor: Claimed and sat on it w/o providing liquidity  
    - token_balance >= CLAIMED_TOKEN_VOLUME
    - amount_bought = 0
    - amount_sold = 0
    - amount_deposited_lp = 0
    
- Dumpooooor: Claimed and sold everything w/o providing liquidity (if received from another EOA, Maximizer)
    - token_balance = 0
    - amount_bought = 0
    - amount_sold >= CLAIMED_TOKEN_VOLUME
    - simple_amount_in = 0 
    - amount_deposited_lp = 0

  - Hedgoooor: Claimed, sold a piece, kept the rest. Never bought, received, provided liquidity
    - token_balance < CLAIMED_TOKEN_VOLUME 
    - token_balance > 0
    - amount_bought = 0
    - amount_sold < CLAIMED_TOKEN_VOLUME
    - amount_sold > 0
    - amount_deposited_lp = 0
    - simple_amount_in = 0

- Exchangooor: Claimed, sent it all to a central exchange; never bought, received, nor provided liquidity
   - token-balance = 0
   - amount_bought = 0 
   - amount_sold = 0
   - cex_transfer_out >= CLAIMED_TOKEN_VOLUME
   - amount_deposited_lp = 0

- Market Maker: Provided liquidity, may or may not have withdrawn and sold later.  
    - amount_deposited_lp > 0 
    
- Trader: Bought and Sold Hop, without having provided liquidity.
    - amount_bought > 0
    - amount_sold > 0
    - amount_deposited_lp = 0
    
- Airdrop Maximizer: Received tokens from another EOA AND sold, never providing liquidity nor buying.
    - amount_bought = 0
    - amount_sold > 0
    - simple_amount_in > 0
    - amount_deposited_lp = 0

- Intermediary: never bought, never provided liquidity; transferred equal or more than it claimed to another EOA. Possibly affiliated with an Airdrop Maximizer.
    - simple_amount_out >= CLAIMED_TOKEN_VOLUME 
    - amount_bought = 0 
    - amount_deposited_lp = 0
    
- Undefined: Anyone else, potentially doing a variety of maneuvers and not cleanly fitting into another category. 


```{r, warning = FALSE, message = FALSE}

hop_merge <- hop_merge %>% mutate(
class = case_when(
  TOKEN_BALANCE >= CLAIMED_TOKEN_VOLUME & 
    amount_bought == 0 & 
    amount_sold == 0 & 
    amount_deposited_lp == 0 ~ "Keepooor",
  TOKEN_BALANCE == 0 & 
    amount_bought == 0 & 
    amount_sold >= CLAIMED_TOKEN_VOLUME & 
    simple_amount_in == 0 &
    amount_deposited_lp == 0 ~ "Dumpooor",
  TOKEN_BALANCE < CLAIMED_TOKEN_VOLUME & 
    TOKEN_BALANCE > 0 &
    amount_bought == 0 & 
    amount_sold < CLAIMED_TOKEN_VOLUME & 
    amount_sold > 0 & 
    amount_deposited_lp == 0 & 
    simple_amount_in == 0 ~ "Hedgooor",
  TOKEN_BALANCE == 0 & 
    amount_bought == 0 & 
    amount_sold == 0 & 
    cex_transfer_out >= CLAIMED_TOKEN_VOLUME & 
    amount_deposited_lp == 0 ~ "Exchangooor",
  amount_deposited_lp > 0 ~ "Market Maker",
  amount_bought > 0 & 
    amount_sold > 0 &
    amount_deposited_lp == 0 ~ "Trader",
  amount_bought == 0 &
    amount_sold > 0 & 
    simple_amount_in > 0 & 
    amount_deposited_lp == 0 ~ "Maximizooor",
  simple_amount_out >= CLAIMED_TOKEN_VOLUME &
    amount_bought == 0 &
    amount_deposited_lp == 0  ~ "Intermediary",
  TRUE ~ "Undefined"
)
)

class_tbl <- as.data.frame(table(hop_merge$class))
colnames(class_tbl) <- c("class", "count")

plot_ly(data = class_tbl, x = ~class, y =~count, type = 'bar') %>% 
  layout(
    xaxis = list(title = "Claimer Class"),
    yaxis = list(title = "# of Claimers in Class"),
    title = list(text = "HOP Airdrop Claimers by Post-Claim Action", y = 0.975)
  )

```

